
\section{Preliminaries}
\subsection{Definitions}
An edge cover of a graph is a set of edges such that every vertex has at least an adjacent edge in it.

Given a graph $G=(V,E)$ with $e \in E$,  we use $EC(G)$ to denote the set of all edge covers of graph $G$, and $P(G, e)$ to denote the marginal probability over $EC(G)$ that edge $e$ is not chosen, or formally, with $X \sim EC(G)$ uniformly,
\begin{equation}
	P(G, e) \triangleq \mathbb{P} \left(\textrm{edge $e$ is not chosen in $X$} \right)
	\label{defpge}
\end{equation}

In this paper, we deal with an extended notion of undirected graphs where dangling edges and free edges may be allowed.
\begin{Def}
	A {\bf dangling edge} $e=(u,\_)$ of a graph is such singleton edge with only one end-point vertex $u$, as shown in the Figure \ref{fig:G}.

	A {\bf free edge} $e=(\_, \_)$ of a graph is such edge with no end-point vertex. Note that a free edge is not a dangling edge.


\end{Def}

	So we use graph to refer graphs with or without dangling edges or free edges.
	Edges in the usual sense (i.e. not dangling and not free), will be referred to as normal edges.
	%and graphs in the usual sense(i.e. graphs with only normal edges) will be refered to as normal graphs.

	We remark that an alternative view to these combinatorial definitions is from Rtw-Mon-CNF.
	A dangling edge is just a variable which only appears at one clause, and a free edge is a variable
	that does not appear at all, whereas normal edge just corresponds to variables appearing twice.

For a graph $G=(V,E)$, an edge $e = (u,v) \in E$ and a vertex $u \in V$,
define
\begin{align*}
G - e &\triangleq (V, E-e) \\
e - u &\triangleq (\_, v) \text{(note that here $v$ could be $\_$)} \\
G - u &\triangleq (V - u, \set{e: e \in E, e\text{ is not incident with }u} \cup \set{e - u: e \in E, e\text{ is incident with }u})
\end{align*}

%For a graph $G=(V,E)$ with an edge (may be dangling or free) $e \in E$ and a vertex $v \in V$,
%$$G-e \triangleq (V, E-e)$$
%and
%\begin{align*}
%G-v \triangleq & (V-\set{v}, \set{(x,y):x \in V-\set{v}, y \in V-\set{v}, (x,y) \in E}  \\
% &\cup \set{(x,\_):x \in V-\set{v}, (v,x) \in E}  \\
% &\cup \set{(\_,\_): (v,\_) \in E \text{ or } (v,v) \in E})
%\end{align*}

Note that here in edge set $E$, duplicates are allowed. We may have multiple dangling edges $(v,\_)$, many free edges $(\_,\_)$ and even parallel edges between two vertices $(u,v)$. For simplicity we treat $(v,\_)$ and $(\_,v)$ as the same.

For example, given a degree-3 vertex $u$ with dangling edge $e$ shown in Figure \ref{fig:G} , the result of $G-e-u$ is shown in Figure \ref{fig:G-e-u} and the result of $e_1 - u$ is shown in Figure \ref{fig:e-u}.

\begin{figure}[htp]
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\setlength{\unitlength}{1mm}
		\begin{picture}(20,20)
			\put(0,0){\circle*{10}}
			\put(0,0){\line(1,1){10}}
			\put(20,0){\circle*{10}}
			\put(20,0){\line(-1,1){10}}
			\put(10,10){\circle*{10}}
			\put(10,10){\line(0,1){10}}
			\put(14,10){$u$}
			\put(8,15){$e$}
			\put(2,6){$e_1$}
			\put(15,5){$e_2$}
		\end{picture}
		\caption{$G$}
		\label{fig:G}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\setlength{\unitlength}{1mm}
		\begin{picture}(20,20)
			\put(0,0){\circle*{10}}
			\put(0,0){\line(0,1){10}}
			\put(20,0){\circle*{10}}
			\put(20,0){\line(0,1){10}}
			\put(2,6){$e_1$}
			\put(15,6){$e_2$}
		\end{picture}
		\caption{$G-e-u$}
		\label{fig:G-e-u}
	\end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
		\centering
		\setlength{\unitlength}{1mm}
		\begin{picture}(20,20)
			\put(0,0){\circle*{10}}
			\put(0,0){\line(0,1){10}}
			\put(20,0){\circle*{10}}
			\put(20,0){\line(-1,1){10}}
			\put(10,10){\circle*{10}}
			\put(10,10){\line(0,1){10}}
			\put(14,10){$u$}
			\put(8,15){$e$}
			\put(2,6){$e_1$}
			\put(15,5){$e_2$}
		\end{picture}
		\caption{$e_1-u$}
		\label{fig:e-u}
	\end{subfigure}
	\caption{Dangling edges examples.}
\end{figure}

We use $0$ to denote scalar value $0$, and $\mathbf{0}$ to denote vector value 0, and $\set{e_i}_{i=1}^{d}$ denote the $d$-dimensional vector with $i$-th coordinate being $e_i$, so $\set{e_i} = \mathbf{0}$ means $\forall i, e_i = 0$.
We also use the convention that when $d=0, \prod_i^d p_i \triangleq 1$.

In general we use $n$ to refer to the number of vertices in a given graph, and $m$ to refer to the number of edges.
